---
title: "p8105_hw5_jy2965"
author: "Jun Yin"
date: "11/8/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))

```



## Problem 1


```{r}
set.seed(10)
iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```


```{r}
#build the function
replace_na_fun = function(vec) {
  
  if (is.numeric(vec)) {
    vec[is.na(vec)] = mean(vec, na.rm = TRUE)
  } else if (is.character(vec)) {
    vec[is.na(vec)] = "virginica"
  } 

}
#using the function with for loop
iris_noneed = vector("list", length = 5)
for (i in 1:5) {
  
  iris_noneed[[i]] = replace_na_fun(iris_with_missing[[i]])
  
}
 
# Apply this function to the columns of iris_with_missing using a map statement
iris_without_missing = map_df(iris_with_missing,replace_na_fun) 

```


I replaeced missiong value based on the instruction and generated a new dataset named iris_withou_missing.



## Problem 2

```{r}
plyr::ldply(.data = "./data/hw5_data.zip", .fun = unzip, exdir= "./")
pb2_data = as.data.frame(list.files(path = "./data/", pattern = "*.csv")) 
colnames(pb2_data)[1] = "file_names"
read_and_tidy = function(file_names){
     read.csv(str_c("./data/", file_names)) 
}
pb2_tidy_data = 
  mutate(pb2_data,subject_data = map(pb2_data$file_names, read_and_tidy)) %>% 
  unnest(subject_data) %>% 
  separate(file_names, into = c("group", "id"), sep = "_") %>% 
  mutate(id = sapply(id, substring, 1,2))

## spagehtti plot
  graph_plot=
    pb2_tidy_data %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "results"
  ) %>% 
   mutate(week_number = sapply(week, substring, 6,6))
  graph_plot %>% 
  ggplot(aes(x = week_number, y = results, group = id, color = id)) +
  geom_line() +
  facet_grid(~ group) +
  labs(
    title = "Observations on Each Subject over Time",
    x = "Week",
    y = "results",
    caption = "Data from a longitudinal study") +
    theme(legend.position = "bottom")

```


As we can see from the graph, the results of control group don't have any increasing or decreasing trend over 8 weeks, but the results of experiment group increased through 8 weeks.
At the beginning of the experiment, the mean of the results of control group is `r mean(filter(graph_plot, group == "con", week_number == "1")$results)`, and the mean of the value of experiment group is `r mean(filter(graph_plot, group == "exp", week_number == "1")$results)`, which are almost the same. However, the value of the experiment group significantly increased over this 8-weeks study, whereas the control group didn't change a lot (actually decreased a little bit). At the end of this study, the mean value of the control group is `r mean(filter(graph_plot, group == "con", week_number == "8")$results)`, and the mean value of the experiment group is `r mean(filter(graph_plot, group == "exp", week_number == "8")$results)`.



## problem 3

```{r}
set.seed(1)
```

```{r}
#create the function of linear regrssion
sim_regression = function(n=30, beta0 = 2, beta1) {
  
  sim_data = tibble(
    x = rnorm(n, mean = 0, sd = 1),
    sigma_square = 50,
    y = beta0 + beta1 * x + rnorm(n, 0, sd = sigma_square)
  )
  
  ls_fit = lm(y ~ x, data = sim_data)
  tibble( 
    beta1_hat = coef(ls_fit)[2],
    p_value = broom::tidy(ls_fit)$p.value[2]
  )
 
}
#using for loop to generate model dataset with different beta1
model_beta1 = vector("list", length = 7)
for (i in 1:7) {
  model_beta1[[i]] = rerun(10000,sim_regression(beta1 = i-1)) %>% 
  bind_rows() 
}

#generate dataset for first plot
plot_model_beta1 = vector("list", length = 7)
for (i in 1:7) {
  plot_model_beta1[[i]]=
  model_beta1[[i]] %>% 
  mutate(reject = ifelse(p_value<0.05, 1, 0)) %>% 
  group_by(reject) %>% 
  summarize(n = n()) %>% 
  mutate(proportion = n/sum(n)) %>% 
  filter(reject==1)
}
proportion_plot = bind_rows(plot_model_beta1)%>% 
mutate(beta1 = c(0,1,2,3,4,5,6))
proportion_plot%>% 
  ggplot(aes(x=beta1, y = proportion))+
  geom_point()+
  geom_line()+
  labs(
     title = "Proportion of rejected H0 over different beta1",
    x = "True beta1",
    y = "Propotion"
  )
```

**Describe the association between effect size and power**

As the effect size increases, the power of a statistical test increases. The effect size, d, is defined as the number of standard deviations between the null mean and the alternate mean. The power is correctly reject the null hypothesis.




```{r}
#second plot
plot2_model_beta1 = vector("list", length = 7)
for (i in 1:7) {
  plot2_model_beta1[[i]]=
  model_beta1[[i]] %>% 
  pivot_longer(beta1_hat,
               names_to = "parameter",
               values_to = "beta1"
               ) %>% 
  group_by(parameter) %>% 
  summarize(mean_beta = mean(beta1))
}
es_vs_true_beta1 = bind_rows(plot2_model_beta1) %>% 
  mutate(true_beta = c(0,1,2,3,4,5,6))
es_vs_true_beta1 %>% 
  ggplot(aes(x = true_beta, y = mean_beta))+
  geom_point()+
  geom_line()+
  labs(
     title = "Average estimate of beta1 VS True beta1",
    x = "True beta1",
    y = "Average estimate of beta1"
  )

#third plot

plot3_model_beta1 = vector("list", length = 7)
for (i in 1:7) {
  plot3_model_beta1[[i]]=
  model_beta1[[i]] %>%
  mutate(reject = ifelse(p_value<0.05, 1, 0)) %>% 
  filter(reject==1) %>% 
  pivot_longer(beta1_hat,
               names_to = "parameter",
               values_to = "beta1"
               ) %>% 
  group_by(parameter) %>% 
  summarize(mean_beta = mean(beta1))
}
es_vs_true_beta1_reject = bind_rows(plot3_model_beta1) %>% 
  mutate(true_beta = c(0,1,2,3,4,5,6))
es_vs_true_beta1_reject %>% 
  ggplot(aes(x = true_beta, y = mean_beta))+
  geom_point()+
  geom_line()+
  labs(
     title = "Average estimate of beta1 VS True beta1 in reject H0 group",
    x = "True beta1",
    y = "Average estimate of beta1"
  )
```

**Is the sample average of β̂ 1 across tests for which the null is rejected approximately equal to the true value of β1? Why or why not?**

No, the sample average of beta1 across tests for which the null is rejected is not approximately equal to the true value of beta1. Because those beta1 in successfully reject null hypothesis group were collected in the rejection area of t-test statistics, which had extreme values different from 0. 