---
title: "p8105_hw5_jy2965"
author: "Jun Yin"
date: "11/8/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(plyr)
library(rvest)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))

```



## Problem 1


```{r}
set.seed(10)
iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```


```{r}
#build the function
replace_na_fun = function(vec) {
  
  if (is.numeric(vec)) {
    vec[is.na(vec)] = mean(vec, na.rm = TRUE)
  } else if (is.character(vec)) {
    vec[is.na(vec)] = "virginica"
  } 
  
 vec
}
#using the function with for loop
iris_noneed = vector("list", length = 5)
for (i in 1:5) {
  
  iris_noneed[[i]] = replace_na_fun(iris_with_missing[[i]])
  
}
 
# Apply this function to the columns of iris_with_missing using a map statement
iris_without_missing = map_df(iris_with_missing,replace_na_fun) 

```


I replaeced missiong value based on the instruction and generated a new dataset named iris_withou_missing.



## Problem 2

```{r}
ldply(.data = "./data/hw5_data.zip", .fun = unzip, exdir= "./")
pb2_data = as.data.frame(list.files(path = "./data/", pattern = "*.csv")) 
colnames(pb2_data)[1] = "file_names"
read_and_tidy = function(file_names){
     read.csv(str_c("./data/", file_names)) 
}
pb2_tidy_data = 
  mutate(pb2_data,subject_data = map(pb2_data$file_names, read_and_tidy)) %>% 
  unnest(subject_data) %>% 
  separate(file_names, into = c("group", "id"), sep = "_") %>% 
  mutate(id = sapply(id, substring, 1,2))

## spagehtti plot
  graph_plot=
    pb2_tidy_data %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "results"
  ) %>% 
   mutate(week_number = sapply(week, substring, 6,6))
  graph_plot %>% 
  ggplot(aes(x = week_number, y = results, group = id, color = id)) +
  geom_line() +
  facet_grid(~ group) +
  labs(
    title = "Observations on Each Subject over Time",
    x = "Week",
    y = "results",
    caption = "Data from a longitudinal study") +
    theme(legend.position = "bottom")

```


As we can see from the graph, the results of control group don't have any increasing or decreasing trend over 8 weeks, but the results of experiment group increased through 8 weeks.
At the beginning of the experiment, the mean of the results of control group is `r mean(filter(graph_plot, group == "con", week_number == "1")$results)`, and the mean of the value of experiment group is `r mean(filter(graph_plot, group == "exp", week_number == "1")$results)`, which are almost the same. However, the value of the experiment group significantly increased over this 8-weeks study, whereas the control group didn't change a lot (actually decreased a little bit). At the end of this study, the mean value of the control group is `r mean(filter(graph_plot, group == "con", week_number == "8")$results)`, and the mean value of the experiment group is `r mean(filter(graph_plot, group == "exp", week_number == "8")$results)`.


